The Inconsistency in G\"odel's Ontological Argument: \\ A Success Story for AI in Metaphysics

### 2016-01-31 Papers/InProgress/IJCAI/submission.tex
Fix convoluted paragraph about empty set notation

\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/LEO-Proof.png}}
\caption{Lines 115--120 of \textsc{Leo-II}'s refutation. Primitive
  substitutions (e.g. with the empty property) are highlighted. In the
red part, property variable $\texttt{SV8}$ has been instantiated with the
$\lambda \texttt{SV16}. \lambda \texttt{SV17}. \bot$, i.e., the empty property.
} \label{LEO-Proof}
\end{figure*}

Although \textsc{Leo-II}'s resolution refutation is not easy to read
for humans, it did contain relevant hints to the importance of the
empty property $\lambda x. \bot$ (respectively $\lambda x. \lambda
y. \bot$ in the embedding approach, cf. Fig.~\ref{LEO-Proof}; the 
additional ``$\lambda y.$'' is due to the formula lifting).
%
Note that the terms for the empty property ($\lambda x. \bot$) and for the property of self-difference ($\lambda x.  x\not=x$) have identical denotations in a logic setting
with full functional and Boolean extensionality as given
here. Nevertheless, some philosophers may actually prefer the use of
self-difference over the empty property\footnote{This occurred in
  a private communication of the authors with Andr\'e Fuhrmann.} in
the analysis below. However, for the proof to go through it is
irrelevant which notion we use and the reader may simply replace the
empty property by self-difference. In HOL it is customary to think of
a set as a unary predicate that is true for (and only for) elements of
the set. Therefore, the empty property (i.e. the unary predicate that
is false for any individual) represents the empty set, and hence we
use the empty set symbol $\emptyset$ as an abbreviation for the empty
property. 
\marginpar{Isabelle proof now uses empty set; the commentary is still convoluted}
%\marginpar{ToDo: should we use the empty set symbol in the isabelle code in figure 5 as well? Or should we instead stop using the empty set symbol in the informal argument (and use $\lambda x. \bot$ instead) and remove this convoluted commentary that I added here.}

>>>>

\begin{figure*}
\centerline{\includegraphics[width=\textwidth]{./Images/LEO-Proof.png}}
\caption{Lines 115--120 of \textsc{Leo-II}'s refutation. Primitive
  substitutions (e.g. with the empty property) are highlighted. In the
red part, property variable $\texttt{SV8}$ has been instantiated with the
$\lambda \texttt{SV16}_{\mu}. \lambda \texttt{SV17}_{\iota}. \bot$, i.e., the (lifted) empty property.
} \label{LEO-Proof}
\end{figure*}

Although \textsc{Leo-II}'s resolution refutation is not easy to read
for humans, it did contain relevant hints to the importance of the
empty property $\lambda x. \bot$ (also denoted $\emptyset$, as in HOL it is customary to think of unary predicates as sets).
%
Note that the terms for the empty property\footnote{An additional lambda abstraction occurs in the empty property in LEO-II's proof (and also in the reconstruction in Isabelle) because the embedding approach lifts the boolean type $o$ to $\iota \imp o$.} ($\lambda x. \bot$) and for the property of self-difference ($\lambda x.  x\not=x$) have identical denotations in a logic setting
with full functional and Boolean extensionality as given
here. Nevertheless, some philosophers may actually prefer the use of
self-difference over the empty property\footnote{This occurred in
  a private communication of the authors with Andr\'e Fuhrmann.} in
the analysis below. However, for the proof to go through it is
irrelevant which notion we use and the reader may simply replace the
empty property by self-difference.
